### 2020-12-04 README.Rmd
functions done
margins ok

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/sheilarm23/rrcompendium/master?urlpath=rstudio)

@@

> Rodriguez-Machado, S. and Rodríguez-Cabrera, T.M. (2020). _The Truth is Revealed: Identity of the Fish Fry "Teti" Fishery in Eastern Cuba_. Name of journal/book <https://doi.org/{DOI-to-paper}>

@@

> Rodriguez-Machado, S. and Rodríguez-Cabrera, T.M. (2020). _The Truth is Revealed: Identity of the Fish Fry "Teti" Fishery in Eastern Cuba_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/{DOI-to-compendium}>

@@

> Rodriguez-Machado, S. (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `The Truth is Revealed: Identity of the Fish Fry "Teti" Fishery in Eastern Cuba`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/{DOI-to-compendium}>

@@

## How to run in your broswer or download and run locally

@@

The simplest way to explore the text, code and data is to click on
[binder](https://mybinder.org/v2/gh/sheilarm23/rrcompendium/master?urlpath=rstudio)
to open an instance of RStudio in your browser, which will have the
compendium files ready to work with. Binder uses rocker-project.org
Docker images to ensure a consistent and reproducible computational
environment. This way will take a few minutes to be ready but you will not need to install any packages on your computer.

You can download the compendium as a zip from from this URL:
[master.zip](https://github.com/sheilarm23/rrcompendium/archive/master.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.Rmd")` in the R console

Makefile:
Whatever the option you choose to explore this compendium, you can also use the makefile (`/analysis/makefile`) in the terminal (`make all`) to compile the .docx document and then, you can use `make clean` to remove all files generated during the process.

>>>>

@@

> Rodriguez-Machado, S. and Rodríguez-Cabrera, T.M. (2020). _The Truth is Revealed: Identity of the Fish Fry "Teti" Fishery in Eastern Cuba_.

@@

> Rodriguez-Machado, S. and Rodríguez-Cabrera, T.M. (2020). _The Truth is Revealed: Identity of the Fish Fry "Teti" Fishery in Eastern Cuba_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`.

@@

> Rodriguez-Machado, S. (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `The Truth is Revealed: Identity of the Fish Fry "Teti" Fishery in Eastern Cuba`_. Accessed `r format(Sys.Date(), "%d %b %Y")`.

@@

## How to download and run locally

@@

You can download the compendium as a zip from from this URL:
[master.zip](https://github.com/sheilarm23/rrcompendium/archive/master.zip). After unzipping:
- open the `.Rproj` file in RStudio
- run `devtools::install()` to ensure you have the packages this analysis depends on (also listed in the
[DESCRIPTION](/DESCRIPTION) file).
- finally, open `analysis/paper/paper.Rmd` and knit to produce the `paper.pdf`, or run `rmarkdown::render("analysis/paper/paper.Rmd")` in the R console

MAKEFILE:
Whatever option you choose to explore, and run, this compendium, you can also use the makefile (`/analysis/makefile`) in the terminal (`make all`) to compile the .docx document and then, you can use `make clean` to remove all files generated during the process.
